Why do we Eval?\\\Large A large-scale study of Eval usage in R

### 2021-03-09 paper/main.tex
Base usage metrics

\paragraph{Base} The base dataset contains 13 packages. All of them trigger at least one \eval call. In total, \baseAllcalls \eval  were recorded. Most of them are calls to he normal \eval. There are a few calls to the other variants, less than 4\%. Contrary to the CRAN dataset, there are calls to \c{evalq} (\baseEvalqs). Out of \baseStaticeval static sites, \baseTriggeredeval are exercised, i.e. \baseTriggeredevalpct. Most of the arguments, \baseCodepercent,  are code objects. However, contrary to CRAN, few, only \baseSymbolpercent, are symbols, but rather language objects, \baseLanguagepercent. There are also few expression objects: \baseExpressionpercent.
The median argument size is \baseMedianszeval, which is more than for CRAN, which we dominated by symbol evaluation, whereas the maximum size is \baseMaxszeval. Small event evals (less than 50 events) amount for \baseSmalleventspct of the events in \eval calls.

@@

\paragraph{Discussion} \emph{Base} is more akin to use \eval for metaprogramming, \emph{kaggle} to evaluate parsed strings, and CRAN is dominated by symbol evaluation. In terms of number of calls, a few calls dominate, with a call from \emph{ggplot} being prominent in the CRAN corpus. When looking at the \eval sites, \eval is more spread out. These two measures emphasize two different points of view:

@@

\section{Power scale of \eval }

>>>>

\paragraph{Base} The base dataset contains 13 packages. All of them trigger at least one \eval call. In total, \baseAllcalls \eval  were recorded. Most of them are calls to he normal \eval. There are a few calls to the other variants, less than 4\%. Contrary to the CRAN dataset, there are calls to \c{evalq} (\baseEvalqs). Out of \baseStaticeval \eval static sites, \baseTriggeredeval are exercised, i.e. \baseTriggeredevalpct, out of \baseStaticevalq, \baseTriggeredevalq are exercised, and out of \baseStaticevalparent, \baseTriggeredevalparent are exercised.  Most of the arguments, \baseCodepercent,  are code objects. However, contrary to CRAN, few, only \baseSymbolpercent, are symbols, but rather language objects, \baseLanguagepercent. There are also few expression objects: \baseExpressionpercent.
The median argument size is \baseMedianszeval, which is more than for CRAN, which was dominated by symbol evaluation.The maximum size is \baseMaxszeval. Small event evals (less than 50 events) amount for \baseSmalleventspct of the events in \eval calls.

@@

\paragraph{Discussion} \emph{Base} is more akin to use \eval for metaprogramming, \emph{kaggle} to evaluate parsed strings, and CRAN is dominated by symbol evaluation. In terms of number of calls, a few calls dominate, with a call from \emph{ggplot} being prominent in the CRAN corpus. When looking at the \eval sites, \eval is more spread out. Those two measures emphasize two different points of view:

@@
